R Programming - Week 1
===================================

```{r echo=FALSE}
library(knitr)
opts_chunk$set(cache=T, echo=T, warning=F, message=F)
```

Download, unzip and load dataset
```{r}
zip_url <- "https://d396qusza40orc.cloudfront.net/rprog%2Fdata%2Fquiz1_data.zip"

temp <- tempfile()
download.file(zip_url,temp)
df <- read.csv(unz(temp, "hw1_data.csv"))
unlink(temp)
```

In the dataset provided for this Quiz, what are the column names of the dataset?
```{r}
names(df)
```
Extract the first 2 rows of the data frame and print them to the console. What does the output look like?
```{r}
head(df, 2)
```
How many observations (i.e. rows) are in this data frame?
```{r}
nrow(df)
```
Extract the last 2 rows of the data frame and print them to the console. What does the output look like?
```{r}
tail(df, 2)
```
What is the value of Ozone in the 47th row?
```{r}
df[47, "Ozone"]
```
How many missing values are in the Ozone column of this data frame?
```{r}
nrow(subset(df, is.na(df$Ozone)))
```
What is the mean of the Ozone column in this dataset? Exclude missing values (coded as NA) from this calculation.
```{r}
mean(df$Ozone, na.rm=TRUE)
```
Extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90. 
What is the mean of Solar.R in this subset?
```{r}
mean(subset(df, df$Ozone > 31 & df$Temp >  90)$Solar.R, na.rm=TRUE)
```
What is the mean of "Temp" when "Month" is equal to 6?
```{r}
mean(subset(df, df$Month == 6)$Temp, na.rm=TRUE)
```
What was the maximum ozone value in the month of May (i.e. Month = 5)?
```{r}
max(subset(df, df$Month == 5)$Ozone, na.rm=TRUE)
```